Open Science, Open Plant Pathology

### 2020-04-22 analysis/paper/paper.Rmd
add more detail to scoring methods

Articles were provided classifications, whether they were fundamental or applied and a note was made whether the article's primary focus was molecular (TRUE/FALSE).

@@

The majority of the articles were classed as fundamental, 160, with 138 classed as applied.

>>>>

Articles were provided classifications, whether they were fundamental or applied and a note was made whether the article's primary focus was molecular (TRUE/FALSE).
This classification was based on the evaluator's own judgement of the article.

Further classification as to whether the articles focused on using or developing molecular techniques was included.

@@

The majority of the articles were classed as fundamental, 160, with 138 classed as applied, nearly an even distribution between the types of article.
